---
title: "Streets"
author: "Martin Kosík"
date: "2 7 2021"
output: html_document
editoroptions: 
  chunk_output_type: console
editor_options: 
  chunk_output_type: console
---


```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(sf)
library(mapview)
library(mapedit)
library(USAboundaries)
library(USAboundariesData)

```


OpenStreetMap data were downloaded (on July 2, 2021) from http://download.geofabrik.de/north-america/us.html



```{r}
sc_roads <- st_read(here::here("maps/confederate_streets/SC/gis_osm_roads_free_1.shp")) #%>% st_set_crs("+proj=longlat +datum=WGS84 +no_defs")

ge_roads <- st_read(here::here("maps/confederate_streets/Georgia/gis_osm_roads_free_1.shp")) 
nc_roads <- st_read(here::here("maps/confederate_streets/NC/gis_osm_roads_free_1.shp")) 

all_roads <- rbind(sc_roads, ge_roads, nc_roads)

rm(list = c('sc_roads', 'ge_roads', 'nc_roads'))
gc()

all_roads <- all_roads %>% 
  dplyr::select(name) %>% 
  dplyr::filter(!is.na(name))

names(all_roads)

counties  <- us_counties(states = c("Georgia", "North Carolina", "South Carolina")) %>% 
  mutate(fips = as.numeric(paste0(statefp, countyfp)))



```

```{r}

all_roads$geometry <- all_roads$geometry %>% 
  st_transform(crs = 26916) %>% 
  st_centroid()


#plot(sc_roads$geometry)

```


Confederate figures:
 Robert E. Lee, Jefferson Davis, Stonewall 
Jackson, P.G.T. Beauregard, Braxton Bragg, Jubal Early, 
Richard Ewell, Nathan Bedford Forrest, A.P. Hill, John B. 
Hood, Wade Hampton, Joseph E. Johnston, Joseph Brevard 
Kershaw, James Longstreet, Robert E. Rodes, J.E.B. Stuart, 
Earl Van Dorn, Raphael Semmes, Nathan G. Evans, George 
Pickett, Matthew Fontaine Maury, Albert Sidney Johnston, 
John Mosby, and Bill Anderson



```{r}



counties_joined <- counties %>% 
  st_transform(crs = 26916) %>% 
  st_join(all_roads)


```


```{r}
counties_joined$geometry <- NULL

counties_joined %>% 
  write_csv(here::here('maps/confederate_streets/streets_joined_with_counties.csv'))


conf_figures <- c("Lee", "Davis", "Forrest", "Stonewall", "Beauregard", "Stonewall", "Ewell",
                  "Hood", "Hampton", "Kershaw", "Rodes", "Van Dorn", 
                  "Longstreet", "Maury", "Mosby")



first_names <- c("Robert", "Jefferson", "Nathan","Stonewall", "P", "Braxton", "Richard", 
                 "John", "Wade", "Joseph", "Robert", "Earl", "James", "Matthew", "John")


last_names <- c("Lee", "Davis", "Forrest", "Stonewall", "Beauregard", "Stonewall", "Ewell",
                  "Hood", "Hampton", "Kershaw", "Rodes", "Van Dorn", 
                  "Longstreet", "Maury", "Mosby")

length(last_names)


str_detect("robert lee", "r.* lee|lll")

str_detect("robert lee", regex("Robert .*Lee  | Jefferson .*Davis", ignore_case=TRUE))


regex_pattern_both <- str_c(' ' ,first_names, ' .*', last_names, ' ', collapse = '|')

str_detect(" robert e. lee street ", pattern = regex(regex_pattern_both, ignore_case=TRUE)) * 1


regex_pattern_only_surname <- str_c(' ' ,conf_figures, ' ', collapse = '|')


" Robert E Lee Street 	"

str_detect("robert e. lee street", pattern = regex(regex_pattern, ignore_case=TRUE)) * 1



counties_joined <- counties_joined %>% 
  mutate(
    street_name = str_c(' ', name.y, ' '), 
    conf_street_surname = str_detect(street_name, pattern = regex(regex_pattern_only_surname, ignore_case=TRUE)) * 1,
    conf_street_both = str_detect(street_name, pattern = regex(regex_pattern_both, ignore_case=TRUE)) * 1,
    )


counties_joined %>% 
  count(conf_street_surname)

counties_joined %>% 
  count(conf_street_both)




counties_joined <- counties_joined %>% 
  group_by(statefp, countyfp) %>% 
  summarise(n_streets = n(),
            conf_streets_surname = sum(conf_street_surname, na.rm = TRUE),
            conf_streets_both = sum(conf_street_both, na.rm = TRUE))


counties_joined %>% 
  write_csv('data/conf_streets_by_county.csv')


```

