---
title: "Streets"
author: "Martin Kosík"
date: "2 7 2021"
output: html_document
editoroptions: 
  chunk_output_type: console
---


```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(sf)
library(mapview)
library(mapedit)
library(USAboundaries)
library(USAboundariesData)

```


OpenStreetMap data were downloaded (on July 2, 2021) from http://download.geofabrik.de/north-america/us.html



```{r}
sherman_march_map <- st_read(here::here("maps/sherman_march/sherman_march_shapefile_v2.shp")) #%>% st_set_crs("+proj=longlat +datum=WGS84 +no_defs")


sc_roads <- st_read(here::here("maps/confederate_streets/SC/gis_osm_roads_free_1.shp")) #%>% st_set_crs("+proj=longlat +datum=WGS84 +no_defs")

counties  <- us_counties(states = c("Georgia", "North Carolina", "South Carolina")) %>% 
  mutate(fips = as.numeric(paste0(statefp, countyfp)))

sc_counties  <- us_counties(states = c("South Carolina")) %>% 
  mutate(fips = as.numeric(paste0(statefp, countyfp)))



```

```{r}

sc_roads$geometry %>% 
  head() %>% 
  st_transform(crs = 26916) %>% 
  st_centroid()

sc_roads$geometry <- sc_roads$geometry %>% 
  st_transform(crs = 26916) %>% 
  st_centroid()


plot(sc_roads$geometry)

```


Confederate figures:
 Robert E. Lee, Jefferson Davis, Stonewall 
Jackson, P.G.T. Beauregard, Braxton Bragg, Jubal Early, 
Richard Ewell, Nathan Bedford Forrest, A.P. Hill, John B. 
Hood, Wade Hampton, Joseph E. Johnston, Joseph Brevard 
Kershaw, James Longstreet, Robert E. Rodes, J.E.B. Stuart, 
Earl Van Dorn, Raphael Semmes, Nathan G. Evans, George 
Pickett, Matthew Fontaine Maury, Albert Sidney Johnston, 
John Mosby, and Bill Anderson


```{r}
conf_figures <- c("Lee", "Davis", "Forrest", "Jackson", "Stonewall", "Beauregard", "Ewell",
                  "Longstreet")
regex_pattern <- str_c(conf_figures, collapse = ' |')

sc_roads <- sc_roads %>% 
  filter(!is.na(name)) %>% 
  mutate(conf_street = str_detect(name, pattern = regex(regex_pattern, ignore_case=TRUE)) * 1)



str_detect(c('lee street'), pattern = regex(regex_pattern, ignore_case=TRUE))

#sc_roads %>% count(conf_street)
sum(sc_roads$conf_street)

```

```{r}

sc_roads_head <- sc_roads %>% head(100000)


sc_counties_joined <- sc_counties %>% 
  st_transform(crs = 26916) %>% 
  st_join(sc_roads )

sc_counties_joined

```


```{r}
sc_counties_joined$geometry <- NULL


sc_counties_joined <- sc_counties_joined %>% 
  group_by(statefp, countyfp) %>% 
  summarise(n_streets = n(),
            conf_streets = sum(conf_street, na.rm = TRUE))


sc_counties_joined

sc_counties_joined$geometry %>% plot()

sc_counties$geometry %>% plot()


```

